---
title: "Assignment"
author: "setlhabi letlhogonolo 202001771"
date: "16/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
```

# 1.1 variables
```{r, message=FALSE,echo=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tm)
library(wordcloud2)
```

## What is the value of " B " after running these command?
```{r}
a <- 5.0
c <- 10
t <- 12
B <- a+c/t

```
The value of b is `r B`

## What type of vector do you get in each of the following?
```{r}
vec_1 <- c(44, 5, 0, "k")
vec_2 <- c(1, 2, 3, FALSE)
vec_3 <- c("a", "b", "c", TRUE)
vec_4 <- c(1, 2, 3, "4")
```
vector 1 is `r typeof(vec_1)`
vector 2 is `r typeof(vec_2)`
vector 3 is `r typeof(vec_3)`
vector 4 is `r typeof(vec_4)`

# 1.2 conditional subsetting

```{r}
vec <- c(141.2741, 141.8392, 140.5730,NA, 141.3571, 139.8689, 
         137.9384, NA,139.6620, 138.2521, 138.8635, 141.3885, NA)

 vec_2 <-which(is.na(vec))
```

###### 1.2.1
vec_1 is `r na.omit(vec)`, the function that i used which is na.omit removes all incomplete cases of a data frames

#### 1.2.2 indices of missing values are in`r vec_2`i used which functions that returns to locations that have NA values

# 1.2.3 
`r is.na(vec)` ,i used is.na function to differentiate missing values and non missing values , missing values are those that are assigned to true.

```{r}
name <- c("Busiswa Mulenga", "Buhle Abraham", "Eddy Malope")
ages <- c(24,25,26)
gender <-c("MALE","FEMALE","FEMALE")
print(data.frame(name,ages,gender))
```

# functions in R

# 2.2

```{r}
df <- read.csv('train.csv')
```

```{r}
input = c(10, 4, 2, 2)
evaluate <- function(input){
  for(i in input){
    mean = mean(input)
  } 
  print(mean)
}
```

#### 2.1 a mean of an input vector is `r mean(input)`

```{r}
g <- c("MALE","FEMALE","FEMALE","MALE","FEMALE","MALE","MALE","FEMALE", "MALE","MALE","FEMALE","MALE","MALE",
"FEMALE","MALE","MALE","MALE")

  
```

```{r}

x <- rnorm(1000, 120, 5)
y <- sample(c("M","F"),size = 1000, replace = TRUE)


df <-cbind(x,y)

df_1 <- cbind.data.frame(x,y)

 
```

#### 3.2.2 `r df`


```{r}

df <- rnorm(100, 120, 5)
df_2 <- sample(c("M","F"),size = 100, replace = TRUE)
plotting_df <- as.data.frame.table(table(df_1))

p <- ggplot(plotting_df, aes(x = df_2, weight = Freq)) +
  
  geom_bar(width = 0.5, fill = "blue") +
  labs(x = "", y = "Frequency", 
       title = "Sample distribution of Male and Female ") +
  theme(plot.title = element_text(hjust = 0.5)) +
  
  geom_text(aes(x = df_2, y = Freq + 1, label = Freq)) 

  

```


